Leveraging Collaboration: A Methodology for the Design of Social Problem-Solving Systems

### 2013-01-28 old stuff/Article.tex
Atualizei com a versão atual do artigo
Também organizei a estrutura de diretórios mais ou menos como
recomendado pelo Diego

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/fill_iter}
\caption{The graph shows the average number of iterations needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{Most Filled} strategy.
}
\label{fig:fill_iter}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/first_iter}
\caption{The graph shows the average number of iterations needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{First Positions} strategy.
}
\label{fig:first_iter}
\end{figure}

@@

In order to test our hypotheses, we repeated our experiments for the same four topologies, this time varying the copy rate and guess rate between $0\%$ and $100\%$ each. From our results for each topology, we plotted two surfaces for each strategy. The first shows the average number of iterations needed for the network to converge to the correct solution, and the second the number of experiments in which every agent obtained the correct solution in the limit of 100 rounds.

@@

\subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}

@@

We have proposed a novel method for artificial social problem-solving that can be used to analyse the consequences of the behaviour observed in humans in collaborative networks. This is a general model that can be applied to simulate different social computing systems centered on diverse problems. Using it, we modelled the Sudoku-solving environment studied by~\cite{farenzena:collabem} and the behaviour of its subjects, in order to analyse their effects on the problem-solving process. We have discovered that, although humans seemed to choose a solution to copy based on its position on the interface, evaluating the neighbours' proposed solutions to select one for copying leads to the correct solution being found sooner and spreading faster throughout the network. Another important conclusion we have reached is that the performance of the network in solving the problem increases when agents copy more. Surprisingly, increasing the chance that the agents will guess when they cannot make a logical move is also beneficial, indicating that the network is successful in filtering incorrect solutions produced by guessing.

With these results in mind, we have proposed some suggestions to improve the performance of a human social problem-solving network, using properties of the graphic interface and topology to encourage human subjects to follow more effective behaviour. In the future, it would be interesting to validate these suggestions through actual experiments with human beings. We also encourage the employment of the proposed method in simulating other experiments conducted with human subjects, using the results obtained to guide the design of new systems of social computation or the redesign of old ones.

>>>>

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/fill_iter}
\caption{The graph shows the average number of rounds needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{Most Filled} strategy.
}
\label{fig:fill_iter}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=1]{ijcai_sudoku/first_iter}
\caption{The graph shows the average number of rounds needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{First Positions} strategy.
}
\label{fig:first_iter}
\end{figure}

@@

In order to test our hypotheses, we repeated our experiments for the same four topologies, this time varying the copy rate and guess rate between $0\%$ and $100\%$ each. From our results for each topology, we plotted two surfaces for each strategy. The first shows the average number of rounds needed for the network to converge to the correct solution, and the second the number of experiments in which every agent obtained the correct solution in the limit of 100 rounds.

@@

\subsection{Copying and Guessing are Beneficial to the Network's Performance}

@@

Collaborative human computation is a growing area of interest as researchers are attracted to the human problem-solving abilities and strategies. However, although a lot of data about human social behaviour can be collected from experiments, it is still difficult to explain that behaviour and its consequences. Knowing the limitations of human strategies is needed to guide the design of social problem-solving systems. We have proposed a novel method for artificial social problem-solving that can be used to analyse the behaviour observed in humans in collaborative networks. This is a general model that can be applied to simulate different social computing systems centred on diverse problems. We used it to model one particular experiment, simulating the strategies employed by humans on it, and obtained a number of interesting results. We have discovered that, although humans seemed to choose a solution to copy based on its position on the interface, evaluating the neighbours' proposed solutions to select one for copying leads to the correct solution being found sooner and spreading faster throughout the network even if the evaluation function employed is naive. Another important conclusion we have reached is that the performance of the network in solving the problem increases when agents copy more. Surprisingly, increasing the chance that the agents will guess when they cannot make a logical move is also beneficial, indicating that the network is successful in filtering incorrect solutions produced by guessing.

With these results in mind, we have proposed some suggestions to improve the performance of a human social problem-solving network, using properties of the graphic interface and topology to encourage human subjects to follow more effective behaviour. These include displaying neighbours with better-evaluated solutions first, to encourage subjects to copy from them, and using topologies with higher local clustering, to encourage a higher frequency of copy. Future developers of collaborative systems can use these points to plan their design in order to take maximum advantage of the problem-solving network. In the future, it would be interesting to validate these suggestions through actual experiments with human beings. We also encourage the employment of the proposed method in simulating other experiments conducted with human subjects, using the results obtained to guide the design of new systems of social computation or the redesign of old ones.
